### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

\stab{\bf (1) Identifying affected balls}. 
We first develop procedure \identifyaffball,
which utilizes auxiliary structures \fb and \bfc, to identify \affballsx.

@@

\sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, and
\bfc is updated accordingly as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).

\identifyaffball first identifies balls with type code $(1, 1)$ and $(1, 0)$ as \affballsx,
\ie $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$, and then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.

@@

\stab{\bf (2) Updating Fragment-Ball matches}. We then update the partial match relations for \affballsx in $\tilde{M}(P,G)$ \wrt $\Delta P$,
by procedure \incmatch.

@@

\stab{\bf (3) Combining Fragment-Ball matches}. Algorithm \incp finally combines the updated partial match relations in \affballsx to get the updated top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$ by procedure \comb. Observe that only the balls from \affballsx that match with all pattern fragments of $P\oplus \Delta P$ can enter the combination process.

@@

\stab{\bf (4) Early return optimization technique}. 
%As introduced in last section, the {\em lazy update manner} accelerates the process to return updated top-$k$ perfect subgraphs by postponing the processing of each unit pattern update.
We propose an optimization technique for \incp to further speed-up the incremental computations, by making use of the top-$k$ semantics.
%
We first define {\em early return} for incremental top-$k$ algorithms, analogous to {\em early termination} for batch top-$k$ algorithms~\cite{FaginLotem03}.

@@

\stab{\bf (5) The complete algorithm for pattern updates}.
Given $\tilde{M}(P,G)$, \fb, \bfc and \upl, for pattern update $\Delta P$,
algorithm \incp computes the maximum match relations of $P \oplus \Delta P$ in $G$ with early return property, and maintains auxiliary structures simultaneously by invoking procedure \identifyaffball, \incmatch and \comb one by one.

>>>>

\stab{\bf (I) Identifying affected balls}. 
We first develop procedure \identifyaffball,
which utilizes auxiliary structures \fb and \bfc, to identify \affballsx.

@@

\sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, \revise{and all four $fc$ in \bfc are updated from $fc$ (1, 1) to $fc_{\Delta}$ (1, 0), as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).}

\revise{Procedure \identifyaffball firstly identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx, 
	since $tc (1, 1) \& fc_{\Delta}(1, 1) = fc_{\Delta}(1, 1)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.}
Then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.

@@

\stab{\bf (II) Updating Fragment-Ball matches}. We then update the partial match relations for \affballsx in $\tilde{M}(P,G)$ \wrt $\Delta P$,
by procedure \incmatch.

@@

\stab{\bf (III) Combining Fragment-Ball matches}. Algorithm \incp finally combines the updated partial match relations in \affballsx to get the updated top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$ by procedure \comb. Observe that only the balls from \affballsx that match with all pattern fragments of $P\oplus \Delta P$ can enter the combination process.

@@

\stab{\bf (IV) Early return optimization technique}. 
%As introduced in last section, the {\em lazy update manner} accelerates the process to return updated top-$k$ perfect subgraphs by postponing the processing of each unit pattern update.
We propose an optimization technique for \incp to further speed-up the incremental computations, by making use of the top-$k$ semantics.
%
We first define {\em early return} for incremental top-$k$ algorithms, analogous to {\em early termination} for batch top-$k$ algorithms~\cite{FaginLotem03}.

@@

\stab{\bf (V) The complete algorithm for pattern updates}.
Given $\tilde{M}(P,G)$, \fb, \bfc and \upl, for pattern update $\Delta P$,
algorithm \incp computes the maximum match relations of $P \oplus \Delta P$ in $G$ with early return property, and maintains auxiliary structures simultaneously by invoking procedure \identifyaffball, \incmatch and \comb one by one.
